---
title: "DV_RProject2"
author: "Zareen Khayrattee, Kayne Khoury, Juanito Taveras"
date: "October 1, 2015"
output: html_document
---

----------------

#Plot 1
The very interesting thing about this workflow is that there are no cumulative distribution of less than .10, or even less than .90 for that matter, meaning that no matter what country you are in, fatalities from respiratory infections in babies less than one month old is a huge problem. However, the risk of death from respiratory infections does decrease as the child gets older for people in most countries, with the very apparent exception of India, where it's still a huge problem in children up to almost 5 years of age. Death of children ages 0-1 month from respiratory infections is plotted on the X-axis, and Death of children ages 1-4 years is plotted on the Y-axis.
```{r}
source("../02 Data Wrangling/DataWrangling_P2.R",echo=TRUE)
```

----------------
#Plot 2
The workflow shows the top ten mortality percentages of children less than one month old for countries with a total number of deaths greater than 100,000. The data first creates a secondary data frame that counts the total deaths for every country for all years. The data is then filtered only to consider countries with more than 100,000 total deaths. Another column is added to calculate the percentage of children that were less than one month old. The table is then arranged in descending order and plotted. Interestingly, amongst the countries with more than 100,000 deaths, the highest percentages less than one month old were either in Africa or Asia.

```{r}
source("../02 Data Wrangling/Data_Wrangling_P3.R",echo=TRUE)
```
